---
title: "R Notebook"
output: html_notebook
---

I've setup the environment with the necessary packages and a pointer to a database.

```{r}
library(tidyverse)
con <- RSQLite::dbConnect(RSQLite::SQLite(), "nycflights.sqlite3")
```


As our first step, we'll pull the data. Maybe I have some SQL code to do this:

```{sql connection=con, output.var = flights}
SELECT * FROM flights WHERE arr_delay > 0 LIMIT 10000
```


I can use the data in R to start exploring and answering questions:

```{r}
flights # this will print the data
summary(flights)
```

Maybe I'm interested in seeing what factors influence arrival delay:

```{r}
flights %>% 
  select(sched_dep_time, air_time, arr_delay) %>% 
  cor() %>% 
  corrplot::corrplot(method = 'ellipse')
```

I can also add a new variable for day of week:

```{r}
flights_subset <- flights %>% 
  mutate(date = lubridate::ymd(paste(year, month, day))) %>% 
  mutate(dow = lubridate::wday(date, label = TRUE)) %>% 
  select(dow, arr_delay, sched_dep_time, air_time)

flights_subset

ggplot(flights_subset, aes(y = arr_delay, x = dow)) + 
  geom_boxplot()

ggplot(flights_subset, aes(y = arr_delay, x = air_time)) + 
  geom_point()

flights_
```



I've observed that there are some outliers in my data ... this will influence the model going forward. But, I'll start with a naive linear model:

$ y = \beta_o + \beta_1 x + \epsilon $

```{r}
m <- lm(arr_delay ~ ., data = flights_subset)
summary(m)
plot(m)
```


Help!! The model diagnostics don't look good.















